\documentclass{ximera}
\title{Disable Rendering}


\begin{document}
\begin{abstract}
    A description of how to disable or hide rendered material - while still executing that code.
\end{abstract}
\maketitle
   
\section*{How to Suppress Content from Rendering.}
    \subsection*{Mechanism of Rendering}
        
        There are a number of ways to do this. Probably the best option is to use one of: the command pdfOnly, the environment prompt or the environment onlineOnly. The prompt environment and pdfonly command functionally do the same thing - they display their contents in the pdf that is compiled, but they do not display their content in the online webpage. For example, the following should appear blank online:
        
        \begin{prompt}
            This is the contents of a prompt environment.
        \end{prompt}
        
        However, above - in the pdf - will be the ``This is the content of a prompt environment'' because we used the following code:
        
        \begin{verbatim}
            \begin{prompt}
                This is the contents of a prompt environment.
            \end{prompt}
        \end{verbatim}

        Similarly the following should be blank online: \pdfOnly{some random content - but this command is usually used to call commands or set configurations that apply only to the pdf output}. But, in the pdf there will be a line of text, since we used the command:\\
        
        \begin{verbatim}
        \pdfOnly{some random content - but this command is usually used to 
        call commands or set configurations that apply only to the pdf output}
        \end{verbatim}
        
        Finally, you can get stuff to compile to the online version, but omit it from the pdf, by using the onlineOnly environment. For example:
        
        \begin{onlineOnly}
            This should only be visible online. At least in theory.
        \end{onlineOnly}
        
        This was generated using the code:
        
        \begin{verbatim}
            \begin{onlineOnly}
                This should only be visible online. At least in theory.
            \end{onlineOnly}
        \end{verbatim}
    
    \subsection*{Any Necessary Content}
        
        
        
    \subsection*{Quirks of Rendering}
        
        
        
    \subsection*{Any Ximera-Specific Optional Arguments}
        
        
        
    \subsection*{Accessibility}
        
        
        
    \subsection*{Potential Problems and Pitfalls}
        
        
        
    \subsection*{Any Best Practices or Advice}
        
        
        
\end{document}